Finding the Most Suitable Code Clone Refactoring Techniques by Mapping Clone Context

### 2019-12-06 cefp/paper.tex
Introduction and background

Several refactoring techniques can be used to reduce duplication in source code. Which refactoring technique to apply depends on where a clone is located and what the relation is between similar code fragments \cite{koni2001scenario}. Subsequent studies have performed statistical measurements on how many clones fall into these location and relation categories \cite{fontana2012duplicated, fontana2015duplicated}.

@@

%We perform statistical measurements on a large corpus of open-source software systems to determine which relation, location and contents category has the most clones. We find that 77\% of clones is found in the bodies of constructors and methods, which indicate clones that can be refactored by applying the ``Extract Method'' refactoring technique. Clones were found in very diverse relations, which indicates that in
We perform statistical measurements on a large corpus of open-source software systems to determine which relation, location and contents category has the most clones. We find that 77\% of clones is found in the bodies of constructors and methods, which indicate clones that can be refactored by applying the ``Extract Method'' refactoring technique. What further techniques apply when refactoring a clone using the ``Extract Method'' technique depends on the relation among its clone instances.

@@

\section{Background}
We use two definitions to argue about code clones~\cite{roy2007survey}:
\\ \textbf{Clone instance}: A single cloned fragment.
\\ \textbf{Clone class}: A set of similar clone instances.

@@

\section{Context Analysis of Clones}\label{chap:contextsetup}
To be able to refactor code clones, CloneRefactor first maps the context of code clones. We define the following aspects of the clone as its context:
\begin{enumerate}
  \item \textbf{Relation:} The relation of clone instances among each other through inheritance.
  \item \textbf{Location:} Where a clone instance occurs in the code.
  \item \textbf{Contents:} The statements/declarations of a clone instance.
\end{enumerate}
We define categories for each of these aspects and enable CloneRefactor to determine the categories of clones.

>>>>

Several refactoring techniques can be used to reduce duplication in source code~\cite{fowler2018refactoring}. Which refactoring technique to apply depends on where a clone is located and what the relation is between similar code fragments \cite{koni2001scenario}. Subsequent studies have performed statistical measurements on how many clones fall into these location and relation categories \cite{fontana2012duplicated, fontana2015duplicated}.

@@

%We perform statistical measurements on a large corpus of open-source software systems to determine which relation, location and contents category has the most clones. We find that 77\% of clones is found in the bodies of constructors and methods, which indicate clones that can be refactored by applying the ``Extract Method'' refactoring technique. Clones were found in very diverse relations, which indicates that in
We perform statistical measurements on a large corpus of open-source software systems to determine which relation, location and contents category has the most clones. We find that a significant portion of clones is found in the bodies of constructors and methods, which indicate clones that can be refactored by applying the ``Extract Method'' refactoring technique. What further techniques apply when refactoring such a clone depends on the relation among its clone instances.

@@

\section{Background}
We use two definitions to argue about code clones~\cite{roy2007survey}:
\\ \textbf{Clone instance}: A single code fragment of which a similar/identical copy exists elsewhere in the codebase.
\\ \textbf{Clone class}: A set of similar/identical clone instances.

@@

\section{Context Analysis of Clones}\label{chap:contextsetup}
We define the following aspects of the clone as its context:
\begin{enumerate}
  \item \textbf{Relation:} The relation of clone instances in a clone class among each other through inheritance.
  \item \textbf{Location:} Where a clone instance occurs in the code.
  \item \textbf{Contents:} The statements/declarations of a clone instance.
\end{enumerate}
We define categories for each of these aspects and enable CloneRefactor to determine the categories of clones.
